\textit{Supplementary materials for}: Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2022-12-31 paper/main.tex
minor typo fixes

    \caption{\textbf{Memory ``fingerprints.'' (order manipulation conditions).}
    The across-participant distributions of clustering scores for each feature
    type ($x$-coordinate) are displayed for each experimental condition
    (color), separately for order manipulation (early, top) and randomly
    ordered (late, bottom) lists. See
    Figures~\fingerprintsRandom~and~\fingerprintsAdaptive~for analogous plots
    for the random (control) and adaptive conditions.}
        \label{fig:fingerprints}
    \end{figure}

>>>>

    \caption{\textbf{Memory ``fingerprints'' (order manipulation conditions).}
    The across-participant distributions of clustering scores for each feature
    type ($x$-coordinate) are displayed for each experimental condition
    (color), separately for order manipulation (early, top) and randomly
    ordered (late, bottom) lists. See
    Figures~\fingerprintsRandom~and~\fingerprintsAdaptive~for analogous plots
    for the random (control) and adaptive conditions.}
        \label{fig:fingerprints}
    \end{figure}

### 2022-12-31 paper/supplement.tex
minor typo fixes

    \caption{\textbf{Memory ``fingerprints.'' (random conditions).}
    The across-participant distributions of clustering scores for each feature
    type ($x$-coordinate) are displayed for each experimental condition
    (color), separately for early (top) and late (bottom) lists.}
        \label{fig:fingerprints-random}
\end{figure}

@@

    \caption{\textbf{Memory ``fingerprints.'' (adaptive conditions).}
    The across-participant distributions of clustering scores for each feature
    type ($x$-coordinate) are displayed for each experimental condition
    (color).}
        \label{fig:fingerprints-adaptive}
\end{figure}

>>>>

    \caption{\textbf{Memory ``fingerprints'' (random conditions).}
    The across-participant distributions of clustering scores for each feature
    type ($x$-coordinate) are displayed for each experimental condition
    (color), separately for early (top) and late (bottom) lists.}
        \label{fig:fingerprints-random}
\end{figure}

@@

    \caption{\textbf{Memory ``fingerprints'' (adaptive conditions).}
    The across-participant distributions of clustering scores for each feature
    type ($x$-coordinate) are displayed for each experimental condition
    (color).}
        \label{fig:fingerprints-adaptive}
\end{figure}
